Gafo-cc visuals

### 2022-07-08 analysis/gafo-cc-visuals.Rmd
run cc model leip and ak on cluster

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  scale_color_colorblind()+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()

@@

```{r}
random <- tibble()

for (j in 1:100) {

for (i in 1:960) {

  chance = abs(i + sample(-960:960,1))

  random <- bind_rows(
    random,
    tibble(location = i, 
           iter = j,
           lower = chance, 
           upper = -chance)
  )
}

}

chance <- random%>%
  group_by(location)%>%
  summarise(lower = mean(lower),
            upper = mean(upper))

data%>%
  group_by(targetcentralityx)%>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2),
         center_lower = -targetcentralityx,
         center_upper = targetcentralityx)%>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community))+
  geom_hline(yintercept = 0, lty = 3, alpha = 0.75)+
  geom_line(aes(x = targetcentralityx, y = center_upper), lty = 1, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = center_lower), lty = 1, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
  geom_point(pch = 1, alpha = 0.5)+
  scale_color_colorblind()+
  #ylim(-1500,1500)+
  theme_minimal()

range(data$targetcentralityx)
```

>>>>

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  scale_color_colorblind(name = "", labels = c("Nigeria", "Namibia", "Sambia", "Namibia", "Germany"))+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "bottom")

```
```{r}
ggsave("../visuals/dev_site.png", width = 5, height = 6, bg = "white")
```

```{r}
data%>%
  group_by(targetcentralityx)%>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2),
         center_lower = -targetcentralityx,
         center_upper = targetcentralityx)%>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community))+
  geom_hline(yintercept = 0, lty = 3, alpha = 0.75)+
  geom_line(aes(x = targetcentralityx, y = center_upper), lty = 1, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = center_lower), lty = 1, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
  geom_point(pch = 1, alpha = 0.5)+
  scale_color_colorblind()+
  #ylim(-1500,1500)+
  theme_minimal()

@@
